Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-03-28 data_appendix_all_years.Rmd
categorical variable recode

hh_2005 <- data_2005 %>% 
  select(hh_id, assist, reason, members, sex, age,
         relation, literacy, register, grade, repeated, depto, urb_rur, income) %>% 
  mutate(year = 2005,
         hh_id = as.numeric(hh_id),
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"))
```
```{r export summary table 2005}
export_summary_table(dfSummary(hh_2005))
```

>>>>

hh_2005 <- data_2005 %>% 
  select(hh_id, assist, reason, members, sex, age,
         relation, literacy, register, grade, repeated, depto, urb_rur, income) %>% 
  mutate(year = 2005,
         hh_id = as.numeric(hh_id),
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"))
```

```{r recoding categorical variables 2005}
hh_2005
reason <- as.factor(c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10))
recode(reason, "1='vacation'; 2 = 'money'; 3 = 'work'; 4 = 'sickness/accident/disability'; 5 ='distance'; 6 = 'finished'; 7 = 'age'; 8 = 'not interested'; 9 = 'housework/childcare'; 10 = 'other'")

```{r export summary table 2005}
export_summary_table(dfSummary(hh_2005))
```
